Competing Bandits: The Perils of Exploration under Competition

### 2018-09-04 paper/content/sim_details.tex
tweak

We fix the sliding window size $M = 100$. We found that low values of $M$ induced too much random noise in the results, and increasing $M$ further did not make a substantial qualitative difference. Unless otherwise noted, all results are reported at $t = 2000$. \gaedit{The simulations are computationally intensive with each experiment, after extensive optimization, usually taking around half a day parallelized over a cluster of 12 CPU cores.}

>>>>

We fix the sliding window size $M = 100$. We found that low values of $M$ induced too much random noise in the results, and increasing $M$ further did not make a substantial qualitative difference. Unless otherwise noted, all results are reported at $t = 2000$. \gaedit{The simulations are computationally intensive with each experiment usually taking around half a day parallelized over a cluster of 12 CPU cores.}
